---
title: "Four Caterpillar Species - FP - Caterpillar Survival"
author: "Kris"
date: "`r Sys.Date()`"
output: 
  html_document: 
      toc: true
      toc_float:
        collapsed: false
        smooth_scroll: true
---
  
# Description

   
# Start
### Import pre-made functions
```{r, warning = FALSE, message = FALSE}
source("C:/Users/kreek001/OneDrive - Wageningen University & Research/R_Scripts/DHARMa_functions.R")
```
  
### Libraries
```{r, warning = FALSE, message = FALSE}
R.version$version.string # prints R version

library(car) #for Anova function
packageVersion("car")
library(emmeans) #for post hoc emmeans
packageVersion("emmeans")
library(multcomp) #for cld function at post hoc analysis
packageVersion("multcomp")
library(multcompView) #for cld function at post hoc analysis
packageVersion("multcompView")
library(ggplot2) #graphs
packageVersion("ggplot2")
library(plyr) #for summary table
packageVersion("plyr")
library(glmmTMB) #for doing glm with many different options
packageVersion("glmmTMB")
library(DHARMa) #for model assumptions
packageVersion("DHARMa")
```
  
## Loading data and processing
### Loading data  
```{r}
data <- read.csv("C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/Data/FP_Caterpillar_weight_per_caterpillar.csv")
```
  
### Removing NAs and sterile treatment 
```{r}
data <- data[complete.cases(data$Survival), ]
```
  
### Defining factors  
```{r}
data$Soil_conditioning <- factor(data$Soil_conditioning, levels = c("CTRL", "Cat"))
data$Caterpillar_species <- as.factor(data$Caterpillar_species)
```
  
# Exploring data
```{r}
str(data)
head(data, 12)
summary(data) #check for outliers
table(data$Caterpillar_species, data$PlantNr, data$Soil_conditioning) #Some plants had two in stead of one caterpillar
```

### average caterpillar species
```{r}
data <- aggregate(data$Survival, by = list(data$Caterpillar_species, data$Soil_conditioning, data$Block_g, data$PlantNr), FUN = mean)
colnames(data) <- c("Caterpillar_species", "Soil_conditioning", "Block_g", "PlantNr", "Survival")
```

### Defining factors new data set
```{r}
data$Soil_conditioning <- factor(data$Soil_conditioning, levels = c("CTRL", "Cat"))
data$Caterpillar_species <- as.factor(data$Caterpillar_species)
```

### Check data structure
```{r}
str(data)
head(data, 12)
summary(data) #check for outliers
table(data$Caterpillar_species, data$PlantNr, data$Soil_conditioning) #Some plants had two in stead of one caterpillar
table(data$Block_g, data$Caterpillar_species, data$Soil_conditioning)
```

## Summary table
### Caterpillar_species
```{r}
DataSum <- ddply(data, c("Caterpillar_species", "Soil_conditioning"), summarize,
            N = sum(!is.na(Survival)), #number of samples
            Mis = sum(is.na(Survival)), #number of missing values
            Mean = round(mean(Survival, na.rm=T),3), #mean
            Median = round(median(Survival, na.rm=T),3), #median
            SD = round(sd(Survival, na.rm=T),3), #standard deviation
            SE = round(sd(Survival, na.rm=T) / sqrt(N),5), #standard error
            LCI = round(Mean - (2*SE),3), #lower confidence interval
            HCI = round(Mean + (2*SE),3)) # upper confidence interval
print(DataSum)
```

## Plot 
```{r, fig.width=10, fig.height=4}
ggplot(data = data,
       mapping = aes(y = Survival, x = Soil_conditioning, fill = Soil_conditioning)) + #Defines the data
  stat_boxplot(aes(y = Survival, x = Soil_conditioning),
               geom = "errorbar",
               linetype = 1,
               width = 0.2) +
  facet_wrap(~ Caterpillar_species, #facet wrap2 needed to color strip
             nrow = 1
             #strip = strip0
             #labeller = labeller(CaterpillarNr = c("4" = "4 Cat", "8" = "8 Cat"))
             ) + # Split data into three graphs, a graph for each caterpillar number
  geom_boxplot(outliers = FALSE) + #Defines that the graph will be a box plot and do not show outliers, this is shown by jitter
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  stat_summary(fun = mean,
               geom = "point",
               size = 1.5,
               color = "gray30",
               fill = "white",
               shape = 23) + #Shows the mean as a white circle
  # geom_segment(aes(x = 0.8, y = 1.11, xend = 2.2, yend = 1.11)) +
  # geom_text(data = DataSum2,
  #           aes(label = Letters, y = 1.15, x = 1.5), # fill out the significant letters
  #           size = 4,
  #           hjust = 0.5,
  #           #position = position_dodge(0.5)
  #          ) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     breaks = seq(0, 1, 0.2), #steps on the y-axis
                     limits = c(0, 1.2)) +   #y limits
  scale_fill_manual(values = c("#882255", "#009E73")) + # Manually change the colors of the bars. You need to define fill in second line of the plot script to get it working; c("#009E73", "#56B4E9")
  ylab("Survival") +    #y-label with Mb in italic
  xlab("Soil treatment") +
  #ggtitle(Stats) +
    theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")
```

# Statistical analysis
## Authographa gamma
### Model
```{r}
lm1 <- glmmTMB(data = data[data$Caterpillar_species == "Ag", ], formula = Survival ~ Soil_conditioning, family = binomial(link = "logit"))
lm2 <- glmmTMB(data = data[data$Caterpillar_species == "Ag", ], formula = Survival ~ Soil_conditioning + (1|Block_g), family = binomial(link = "logit"))

glm1 <- glmmTMB(data = data[data$Caterpillar_species == "Ag", ], formula = Survival ~ Soil_conditioning, family = betabinomial(link = "logit"))
glm2 <- glmmTMB(data = data[data$Caterpillar_species == "Ag", ], formula = Survival ~ Soil_conditioning + (1|Block_g), family = betabinomial(link = "logit"))
```

### Model assumptions
```{r, fig.width=10, fig.height=7}
DHARMa.sum(Model = lm1)
DHARMa.sum(Model = lm2)

DHARMa.sum(Model = glm1)
DHARMa.sum(Model = glm2)
```

### Model output
```{r}
summary(lm2)
an_Ag <- Anova(lm2)
an_Ag
```

   
## Mamestra brassicae
### Model
```{r}
lm1 <- glmmTMB(data = data[data$Caterpillar_species == "Mb", ], formula = Survival ~ Soil_conditioning, family = binomial(link = "logit"))
lm2 <- glmmTMB(data = data[data$Caterpillar_species == "Mb", ], formula = Survival ~ Soil_conditioning + (1|Block_g), family = binomial(link = "logit"))

glm1 <- glmmTMB(data = data[data$Caterpillar_species == "Mb", ], formula = Survival ~ Soil_conditioning, family = betabinomial(link = "logit"))
glm2 <- glmmTMB(data = data[data$Caterpillar_species == "Mb", ], formula = Survival ~ Soil_conditioning + (1|Block_g), family = betabinomial(link = "logit"))
```

### Model assumptions
```{r, fig.width=10, fig.height=7}
DHARMa.sum(Model = lm1)
DHARMa.sum(Model = lm2)

DHARMa.sum(Model = glm1)
DHARMa.sum(Model = glm2)
```

### Model output
```{r}
summary(lm2)
an_Mb <- Anova(lm2)
an_Mb
```


## Pieris brassicae
100% survival, no differences between soil treatments

<!-- ### Model -->
<!-- ```{r} -->
<!-- lm1 <- glmmTMB(data = data[data$Caterpillar_species == "Pb", ], formula = Survival ~ Soil_conditioning, family = binomial(link = "logit")) -->
<!-- lm2 <- glmmTMB(data = data[data$Caterpillar_species == "Pb", ], formula = Survival ~ Soil_conditioning + (1|Block_g), family = binomial(link = "logit")) -->

<!-- glm1 <- glmmTMB(data = data[data$Caterpillar_species == "Pb", ], formula = Survival ~ Soil_conditioning, family = betabinomial(link = "logit")) -->
<!-- glm2 <- glmmTMB(data = data[data$Caterpillar_species == "Pb", ], formula = Survival ~ Soil_conditioning + (1|Block_g), family = betabinomial(link = "logit")) -->
<!-- ``` -->

<!-- ### Model assumptions -->
<!-- ```{r, fig.width=10, fig.height=7} -->
<!-- DHARMa.sum(Model = lm1) -->
<!-- DHARMa.sum(Model = lm2) -->

<!-- DHARMa.sum(Model = glm1) -->
<!-- DHARMa.sum(Model = glm2) -->
<!-- ``` -->

<!-- ### Model output -->
<!-- ```{r} -->
<!-- # summary(lm1) -->
<!-- # Anova(lm1) -->
<!-- # summary(lm2) -->
<!-- # Anova(lm2) -->

<!-- # summary(glm1) -->
<!-- # Anova(glm1) -->
<!-- # summary(glm2) -->
<!-- # Anova(glm2) -->
<!-- ``` -->


## Plutella xylostella
### Model
```{r}
lm1 <- glmmTMB(data = data[data$Caterpillar_species == "Px", ], formula = Survival ~ Soil_conditioning, family = binomial(link = "logit"))
lm2 <- glmmTMB(data = data[data$Caterpillar_species == "Px", ], formula = Survival ~ Soil_conditioning + (1|Block_g), family = binomial(link = "logit"))

glm1 <- glmmTMB(data = data[data$Caterpillar_species == "Px", ], formula = Survival ~ Soil_conditioning, family = betabinomial(link = "logit"))
glm2 <- glmmTMB(data = data[data$Caterpillar_species == "Px", ], formula = Survival ~ Soil_conditioning + (1|Block_g), family = betabinomial(link = "logit"))
```

### Model assumptions
```{r, fig.width=10, fig.height=7}
DHARMa.sum(Model = lm1)
DHARMa.sum(Model = lm2)

DHARMa.sum(Model = glm1)
DHARMa.sum(Model = glm2)
```

### Model output
```{r}
summary(lm2)
an_Px <- Anova(lm2)
an_Px
```

### Combine statistics
```{r}
an_mod <- as.data.frame(rbind(an_Ag, an_Mb, an_Px))
an_mod$Cat <- c("A. gamma", "M. brassicae", "P. xylostella")
an_mod

Stats_FP_Cat_Survival <- an_mod
write.csv(Stats_FP_Cat_Survival, "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Statistical output/Stats_FP_Cat_Survival.csv")
```

## All four caterpillar species
### Model
```{r}
lm1 <- glmmTMB(data = data, formula = Survival ~ Soil_conditioning*Caterpillar_species, family = binomial(link = "logit"))
lm2 <- glmmTMB(data = data, formula = Survival ~ Soil_conditioning*Caterpillar_species + (1|Block_g), family = binomial(link = "logit"))

glm1 <- glmmTMB(data = data, formula = Survival ~ Soil_conditioning*Caterpillar_species, family = betabinomial(link = "logit"))
glm2 <- glmmTMB(data = data, formula = Survival ~ Soil_conditioning*Caterpillar_species + (1|Block_g), family = betabinomial(link = "logit"))
```

### Model assumptions
```{r, fig.width=10, fig.height=7}
DHARMa.sum(Model = lm1)
DHARMa.sum(Model = lm2)

DHARMa.sum(Model = glm1)
DHARMa.sum(Model = glm2)
```

### Model output
```{r}
summary(lm2)
Anova(lm2)
```

### Post hoc test
```{r}
# EMMA2 <- emmeans(lm6, pairwise ~ Soil_conditioning*Caterpillar_species, adjust = "tukey", type = "response") # more stringed
# EMA <- cld(EMMA2, Letters = letters)
# EMA
```


# Final figure
## Data preperation
```{r, fig.width=10, fig.height=4}
# Statistical info main effects
Stats_Ag <- paste0("GLMM: p = 0.925")
Stats_Mb <- paste0("GLMM: p = 1")
Stats_Pb <- paste0(" ")
Stats_Px <- paste0("GLMM: p = 0.217")
Stats_All <- paste0("GLMM: Cat sp. p = 0.756; Soil p = 0.299; interaction p = 0.928")

DataSum_Mb <- data.frame(Soil_conditioning = c("Cat", "CTRL"),
                         Letters = c("a", "b"))

colnames(DataSum)[5] <- "Survival"
```

## Autographa gamma
```{r, fig.width=3, fig.height=4}
ggplot(data = data[data$Caterpillar_species == "Ag", ],
       mapping = aes(y = Survival, x = Soil_conditioning)) +
  geom_errorbar(data = DataSum[DataSum$Caterpillar_species == "Ag", ], 
                aes(ymin = Survival - SE, ymax = Survival + SE, color = Soil_conditioning), 
                linewidth = 1,
                width = 0.3) +
  geom_point(data = DataSum[DataSum$Caterpillar_species == "Ag", ],
             aes(y = Survival, x = Soil_conditioning, color = Soil_conditioning),
             size = 2) +
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  # geom_segment(aes(x = 0.8, y = 1.05, xend = 2.2, yend = 1.05)) +
  # geom_text(data = DataSum2,
  #           aes(label = Letters, y = 1.1, x = 1.5), # fill out the significant letters
  #           size = 4,
  #           #position = position_dodge(0.5),
  #           hjust = 0.5) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     breaks = seq(0, 1, 0.25), #steps on the y-axis
                     limits = c(0, 1.05)) +   #y limits
  scale_color_manual(values = c("CTRL" = "#882255", "Cat" = "#009E73")) +  
  ylab("Caterpillar survival") +    #y-label with Mb in italic
  xlab("Soil treatment") +
  ggtitle(Stats_Ag) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")

mapply(function(x)
  ggsave(plot = last_plot(),
         filename = x,
         path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
         scale = 2.2,
         width = 2.5,
         height = 4,
         units = "cm",
         dpi = 300),
  x = c("FP_CatSurvival_Ag.svg", "FP_CatSurvival_Ag.png"))
```

## Mamestra brassicae
```{r, fig.width=3, fig.height=4}
ggplot(data = data[data$Caterpillar_species == "Mb", ],
       mapping = aes(y = Survival, x = Soil_conditioning)) +
  geom_errorbar(data = DataSum[DataSum$Caterpillar_species == "Mb", ], 
                aes(ymin = Survival - SE, ymax = Survival + SE, color = Soil_conditioning), 
                linewidth = 1,
                width = 0.3) +
  geom_point(data = DataSum[DataSum$Caterpillar_species == "Mb", ],
             aes(y = Survival, x = Soil_conditioning, color = Soil_conditioning),
             size = 2) +
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  # geom_segment(aes(x = 0.8, y = 1.05, xend = 2.2, yend = 1.05)) +
  # geom_text(data = DataSum2,
  #           aes(label = Letters, y = 1.1, x = 1.5), # fill out the significant letters
  #           size = 4,
  #           #position = position_dodge(0.5),
  #           hjust = 0.5) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     breaks = seq(0, 1, 0.25), #steps on the y-axis
                     limits = c(0, 1.05)) +   #y limits
  scale_color_manual(values = c("CTRL" = "#882255", "Cat" = "#009E73")) +  
  ylab("Caterpillar survival") +    #y-label with Mb in italic
  xlab("Soil treatment") +
  ggtitle(Stats_Mb) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")

mapply(function(x)
  ggsave(plot = last_plot(),
         filename = x,
         path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
         scale = 2.2,
         width = 2.5,
         height = 4,
         units = "cm",
         dpi = 300),
  x = c("FP_CatSurvival_Mb.svg", "FP_CatSurvival_Mb.png"))
```

## Pieris brassicae
```{r, fig.width=3, fig.height=4}
ggplot(data = data[data$Caterpillar_species == "Pb", ],
       mapping = aes(y = Survival, x = Soil_conditioning)) +
  geom_errorbar(data = DataSum[DataSum$Caterpillar_species == "Pb", ], 
                aes(ymin = Survival - SE, ymax = Survival + SE, color = Soil_conditioning), 
                linewidth = 1,
                width = 0.3) +
  geom_point(data = DataSum[DataSum$Caterpillar_species == "Pb", ],
             aes(y = Survival, x = Soil_conditioning, color = Soil_conditioning),
             size = 2) +
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  # geom_segment(aes(x = 0.8, y = 1.05, xend = 2.2, yend = 1.05)) +
  # geom_text(data = DataSum2,
  #           aes(label = Letters, y = 1.1, x = 1.5), # fill out the significant letters
  #           size = 4,
  #           #position = position_dodge(0.5),
  #           hjust = 0.5) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     breaks = seq(0, 1, 0.25), #steps on the y-axis
                     limits = c(0, 1.05)) +   #y limits
  scale_color_manual(values = c("CTRL" = "#882255", "Cat" = "#009E73")) +  
  ylab("Caterpillar survival") +    #y-label with Mb in italic
  xlab("Soil treatment") +
  ggtitle(Stats_Pb) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")

mapply(function(x)
  ggsave(plot = last_plot(),
         filename = x,
         path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
         scale = 2.2,
         width = 2.5,
         height = 4,
         units = "cm",
         dpi = 300),
  x = c("FP_CatSurvival_Pb.svg", "FP_CatSurvival_Pb.png"))
```

## Plutella xylostella
```{r, fig.width=3, fig.height=4}
ggplot(data = data[data$Caterpillar_species == "Px", ],
       mapping = aes(y = Survival, x = Soil_conditioning)) +
  geom_errorbar(data = DataSum[DataSum$Caterpillar_species == "Px", ], 
                aes(ymin = Survival - SE, ymax = Survival + SE, color = Soil_conditioning), 
                linewidth = 1,
                width = 0.3) +
  geom_point(data = DataSum[DataSum$Caterpillar_species == "Px", ],
             aes(y = Survival, x = Soil_conditioning, color = Soil_conditioning),
             size = 2) +
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  # geom_segment(aes(x = 0.8, y = 1.05, xend = 2.2, yend = 1.05)) +
  # geom_text(data = DataSum2,
  #           aes(label = Letters, y = 1.1, x = 1.5), # fill out the significant letters
  #           size = 4,
  #           #position = position_dodge(0.5),
  #           hjust = 0.5) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     breaks = seq(0, 1, 0.25), #steps on the y-axis
                     limits = c(0, 1.05)) +   #y limits
  scale_color_manual(values = c("CTRL" = "#882255", "Cat" = "#009E73")) +  
  ylab("Caterpillar survival") +    #y-label with Mb in italic
  xlab("Soil treatment") +
  ggtitle(Stats_Px) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")

mapply(function(x)
  ggsave(plot = last_plot(),
         filename = x,
         path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
         scale = 2.2,
         width = 2.5,
         height = 4,
         units = "cm",
         dpi = 300),
  x = c("FP_CatSurvival_Px.svg", "FP_CatSurvival_Px.png"))
```

## All caterpillar species
```{r, fig.width=6, fig.height=4}
ggplot(data = data,
       mapping = aes(y = Survival, x = Soil_conditioning)) +
  geom_errorbar(data = DataSum, 
                aes(ymin = Survival - SE, ymax = Survival + SE, color = Soil_conditioning), 
                linewidth = 1,
                width = 0.3) +
  geom_point(data = DataSum,
             aes(y = Survival, x = Soil_conditioning, color = Soil_conditioning),
             size = 2) +
  facet_wrap(~ Caterpillar_species,
             nrow = 1) +
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  # geom_segment(aes(x = 0.8, y = 1.05, xend = 2.2, yend = 1.05)) +
  # geom_text(data = DataSum2,
  #           aes(label = Letters, y = 1.1, x = 1.5), # fill out the significant letters
  #           size = 4,
  #           #position = position_dodge(0.5),
  #           hjust = 0.5) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     breaks = seq(0, 1, 0.25), #steps on the y-axis
                     limits = c(0, 1.05)) +   #y limits
  scale_color_manual(values = c("CTRL" = "#882255", "Cat" = "#009E73")) +  
  ylab("Caterpillar survival") +    #y-label with Mb in italic
  xlab("Soil treatment") +
  ggtitle(Stats_All) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")
# 
# mapply(function(x)
#   ggsave(plot = last_plot(),
#          filename = x,
#          path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
#          scale = 2.2,
#          width = 2.5,
#          height = 4,
#          units = "cm",
#          dpi = 300),
#   x = c("FP_CatSurvival_All.svg", "FP_CatSurvival_All.png"))
```
