---
title: "Three Aphid Species - FP - Population growth"
author: "Kris"
date: "`r Sys.Date()`"
output: 
  html_document: 
      toc: true
      toc_float:
        collapsed: false
        smooth_scroll: true
---
  
# Description

   
# Start
### Import pre-made functions
```{r, warning = FALSE, message = FALSE}
source("C:/Users/kreek001/OneDrive - Wageningen University & Research/R_Scripts/DHARMa_functions.R")
```
  
### Libraries
```{r, warning = FALSE, message = FALSE}
R.version$version.string # prints R version

library(car) #for Anova function
packageVersion("car")
library(emmeans) #for post hoc emmeans
packageVersion("emmeans")
library(multcomp) #for cld function at post hoc analysis
packageVersion("multcomp")
library(multcompView) #for cld function at post hoc analysis
packageVersion("multcompView")
library(ggplot2) #graphs
packageVersion("ggplot2")
library(plyr) #for summary table
packageVersion("plyr")
library(ggh4x) #for coloring strip facet wrap
packageVersion("ggh4x")
library(glmmTMB) #for doing glm with many different options
packageVersion("glmmTMB")
library(DHARMa) #for glm with random factor as alternative to glmmTMB
packageVersion("DHARMa")
```
  
## Loading data and processing
### Loading data  
```{r}
data <- read.csv("C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/Data/FP_Aphid_Population_Growth.csv")
```
  
### Removing NAs and sterile treatment 
```{r}
data <- data[complete.cases(data$Aphid_number), ]
```
  
### Defining factors  
```{r}
data$Soil_conditioning <- factor(data$Soil_conditioning, levels = c("CTRL", "Aphid"))
data$Aphid_species <- as.factor(data$Aphid_species)
```
  
# Exploring data
```{r}
str(data)
head(data, 12)
summary(data) #check for outliers
table(data$Block_g, data$Aphid_species, data$Soil_conditioning)
table(data$cagenr, data$Aphid_species, data$Soil_conditioning)
```

## Summary table
### Aphid_species
```{r}
DataSum <- ddply(data, c("Aphid_species", "Soil_conditioning"), summarize,
            N = sum(!is.na(Aphid_number)), #number of samples
            Mis = sum(is.na(Aphid_number)), #number of missing values
            Mean = round(mean(Aphid_number, na.rm=T),3), #mean
            Median = round(median(Aphid_number, na.rm=T),3), #median
            SD = round(sd(Aphid_number, na.rm=T),3), #standard deviation
            SE = round(sd(Aphid_number, na.rm=T) / sqrt(N),5), #standard error
            LCI = round(Mean - (2*SE),3), #lower confidence interval
            HCI = round(Mean + (2*SE),3)) # upper confidence interval
print(DataSum)
```

## Plot 
```{r, fig.width=8, fig.height=4}
ggplot(data = data,
       mapping = aes(y = Aphid_number, x = Soil_conditioning, fill = Soil_conditioning)) + #Defines the data
  stat_boxplot(aes(y = Aphid_number, x = Soil_conditioning), #Shows the error bars (should be added before box plots to have bars behind box plots)
               geom = "errorbar",
               linetype = 1,
               width = 0.2) +
  facet_wrap(~ Aphid_species + Days_after_inf,
             nrow = 1,
             #labeller = labeller(CaterpillarNr = c("4" = "4 Cat", "8" = "8 Cat"))
             ) + # Split data into three graphs, a graph for each caterpillar number
  geom_boxplot(outliers = FALSE) + #Defines that the graph will be a box plot and do not show outliers, this is shown by jitter
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  stat_summary(fun = mean,
               geom = "point",
               size = 1.5,
               color = "white",
               shape = 18) + #Shows the mean as a white circle
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     #breaks = seq(0, 1, 0.25), #steps on the y-axis
                     limits = c(0, max(data$Aphid_number*1.1))) +   #y limits
  scale_fill_manual(values = c("#56B4E9", "#009E73")) + # Manually change the colors of the bars. You need to define fill in second line of the plot script to get it working; c("#009E73", "#56B4E9")
  ylab("Total number of aphids") +    #y-label with Mp in italic
  xlab("Soil treatment") +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(), #no border around the graph (for border, use: element_rect(color = "gray30", fill = NA))
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 9, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        legend.position = "none")
```


# Statistical analysis
## All four aphid species day 8
### Model
```{r}
glmp1 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species, family = poisson(link = "log"))
glmp2 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr), family = poisson(link = "log"))
glmp3 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr) + (1|Block_g), family = poisson(link = "log"))

glmn1.1 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species, family = nbinom1(link = "log"))
glmn1.2 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr), family = nbinom1(link = "log"))
glmn1.3 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr) + (1|Block_g), family = nbinom1(link = "log"))

glmn2.1 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species, family = nbinom2(link = "log"))
glmn2.2 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr), family = nbinom2(link = "log"))
glmn2.3 <- glmmTMB(data = data[data$Days_after_inf == 8, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr) + (1|Block_g), family = nbinom2(link = "log"))
```

### Model assumptions
```{r, fig.width=10, fig.height=7}
DHARMa.sum(Model = glmp1)
DHARMa.sum(Model = glmp2)
DHARMa.sum(Model = glmp3)

DHARMa.sum(Model = glmn1.1)
DHARMa.sum(Model = glmn1.2)
DHARMa.sum(Model = glmn1.3)

DHARMa.sum(Model = glmn2.1)
DHARMa.sum(Model = glmn2.2)
DHARMa.sum(Model = glmn2.3)
```

### Model output
```{r}
summary(glmn2.3)
an_mod <- Anova(glmn2.3)
an_mod 

Stats_FP_Aphid_PopGrowth_Day8 <- as.data.frame(an_mod)
write.csv(Stats_FP_Aphid_PopGrowth_Day8, "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Statistical output/Stats_FP_Aphid_PopGrowth_Day8.csv")
```

### Post hoc test
```{r}
EMMA <- emmeans(glmn2.3, pairwise ~ Aphid_species, adjust = "tukey")
EMMA
cld(EMMA, Letters = letters)
```

## All four aphid species day 14
### Model
```{r}
glmp1 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species, family = poisson(link = "log"))
glmp2 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr), family = poisson(link = "log"))
glmp3 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr) + (1|Block_g), family = poisson(link = "log"))

glmn1.1 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species, family = nbinom1(link = "log"))
glmn1.2 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr), family = nbinom1(link = "log"))
glmn1.3 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr) + (1|Block_g), family = nbinom1(link = "log"))

glmn2.1 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species, family = nbinom2(link = "log"))
glmn2.2 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr), family = nbinom2(link = "log"))
glmn2.3 <- glmmTMB(data = data[data$Days_after_inf == 14, ], formula = Aphid_number ~ Soil_conditioning*Aphid_species + (1|plantnr) + (1|Block_g), family = nbinom2(link = "log"))
```

### Model assumptions
```{r, fig.width=10, fig.height=7}
DHARMa.sum(Model = glmp1)
DHARMa.sum(Model = glmp2)
DHARMa.sum(Model = glmp3)

DHARMa.sum(Model = glmn1.1)
DHARMa.sum(Model = glmn1.2)
DHARMa.sum(Model = glmn1.3)

DHARMa.sum(Model = glmn2.1)
DHARMa.sum(Model = glmn2.2)
DHARMa.sum(Model = glmn2.3)
```

### Model output
```{r}
summary(glmn2.3)
an_mod2 <- Anova(glmn2.3)
an_mod2

Stats_FP_Aphid_PopGrowth_Day14 <- as.data.frame(an_mod2)
write.csv(Stats_FP_Aphid_PopGrowth_Day14, "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Statistical output/Stats_FP_Aphid_PopGrowth_Day14.csv")
```

### Post hoc test
```{r}
EMMA <- emmeans(glmn2.3, pairwise ~ Aphid_species, adjust = "tukey")
EMMA
cld(EMMA, Letters = letters)
```


## All four aphid species day 8 and 14
### Model
```{r}
glmp1 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf, family = poisson(link = "log"))
glmp2 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf + (1|plantnr), family = poisson(link = "log"))
glmp3 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf + (1|plantnr) + (1|Block_g), family = poisson(link = "log"))

glmn1.1 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf, family = nbinom1(link = "log"))
glmn1.2 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf + (1|plantnr), family = nbinom1(link = "log"))
glmn1.3 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf + (1|plantnr) + (1|Block_g), family = nbinom1(link = "log"))

glmn2.1 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf, family = nbinom2(link = "log"))
glmn2.2 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf + (1|plantnr), family = nbinom2(link = "log"))
glmn2.3 <- glmmTMB(data = data, formula = Aphid_number ~ Soil_conditioning*Aphid_species*Days_after_inf + (1|plantnr) + (1|Block_g), family = nbinom2(link = "log"))
```

### Model assumptions
```{r, fig.width=10, fig.height=7}
DHARMa.sum(Model = glmp1)
DHARMa.sum(Model = glmp2)
DHARMa.sum(Model = glmp3)

DHARMa.sum(Model = glmn1.1)
DHARMa.sum(Model = glmn1.2)
DHARMa.sum(Model = glmn1.3)

DHARMa.sum(Model = glmn2.1)
DHARMa.sum(Model = glmn2.2)
DHARMa.sum(Model = glmn2.3)
```


### Post hoc test
```{r}
EMMA <- emmeans(glmn2.3, pairwise ~ Aphid_species|Days_after_inf, adjust = "tukey")
EMMA
cld(EMMA, Letters = letters)
```

# Final figure
## Data preperation
```{r, fig.width=10, fig.height=4}
Stats_All_8d <- paste0("GLMM: Aphid species p < 0.001; Soil p = 0.257; \nInteraction p = 0.437")
Stats_All_14d <- paste0("GLMM: Aphid species p = 0.001; Soil p = 0.593; \nInteraction p = 0.278")
Stats_All_8_14d <- paste0("GLMM: Aphid species p < 0.001; Soil p = 0.293; Aphid:Soil p = 0.112; \nAphid:Day p = 0.007; Soil:Day p = 0.464; Apid:Soil:Day p = 0.969")

DataSum_All_8d <- data.frame(Aphid_species = rep(c("Bb","Mp", "MpN"), each = 2),
                                Soil_conditioning = rep(c("CTRL", "Aphid"), times = 3),
                                Letters = c("a", "", "b", "", "a", ""))

DataSum_All_14d <- data.frame(Aphid_species = rep(c("Bb","Mp", "MpN"), each = 2),
                                Soil_conditioning = rep(c("CTRL", "Aphid"), times = 3),
                                Letters = c("a", "", "a", "", "b", ""))

DataSum_All_8_14d <- data.frame(Aphid_species = rep(c("Bb", "Mp", "MpN"), each = 4),
                                Days_after_inf = rep(c(8, 8, 14, 14), times = 3),
                                Soil_conditioning = rep(c("CTRL", "Aphid"), times = 6),
                                Letters = c("a", "", "A", "", "b", "", "A", "", "a", "", "B", ""),
                                Height = rep(c(18, 18, 51, 51), times = 3))

# Alter color facet wrap label
strip0 <- strip_themed(background_x = elem_list_rect(fill = c("#BBBBBB", "#A3BE8C", "#CC79A7"))
                        #text_x = elem_list_text(colour = c(rep("white", 5), rep("black", 7)))
                       )
```

## All aphid species 8 days
```{r, fig.width=5, fig.height=4}
ggplot(data = data[data$Days_after_inf == 8, ],
       mapping = aes(y = Aphid_number, x = Soil_conditioning, fill = Soil_conditioning)) +
  stat_boxplot(aes(y = Aphid_number, x = Soil_conditioning), 
               geom = "errorbar",
               linetype = 1,
               width = 0.2) +
  geom_boxplot(outliers = FALSE) + #do not show outliers, this is shown by jitter
  facet_wrap2(~ Aphid_species,
             nrow = 1,
             strip = strip0,
             labeller = labeller(Aphid_species = c(Bb = "Bb", Mp = "gMp", MpN = "rMp"))) +
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  stat_summary(fun = mean,
               geom = "point",
               size = 1.5,
               color = "gray30",
               fill = "white",
               shape = 23) + #Shows the mean as a white circle
  geom_segment(aes(x = 0.8, y = 13, xend = 2.2, yend = 13)) +
  geom_text(data = DataSum_All_8d,
            aes(label = Letters, y = 14, x = Soil_conditioning), # fill out the significant letters
            size = 4,
            hjust = -3,
            #position = position_dodge(0.9)
           ) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     #breaks = seq(0, 25, 5), #steps on the y-axis
                     limits = c(0, 1.25*max(data = data[data$Days_after_inf == 8, "Aphid_number"]))) +   #y limits
  scale_fill_manual(values = c("#882255", "#009E73")) + # Manually change the colors of the bars. You need to define fill in second line of the plot script to get it working; c("#009E73", "#56B4E9")
  ylab("Number of aphids on day 8") +    #y-label with Mp in italic
  xlab("Soil treatment") +
  ggtitle(Stats_All_8d) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")

mapply(function(x)
  ggsave(plot = last_plot(),
         filename = x,
         path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
         scale = 2.2,
         width = 5,
         height = 4,
         units = "cm",
         dpi = 300),
  x = c("FP_Aphid_number_All_8d.svg", "FP_Aphid_number_All_8d.png"))
```

### 8 days - axis as for 14 days
```{r, fig.width=5, fig.height=4}
ggplot(data = data[data$Days_after_inf == 8, ],
       mapping = aes(y = Aphid_number, x = Soil_conditioning, fill = Soil_conditioning)) +
  stat_boxplot(aes(y = Aphid_number, x = Soil_conditioning), 
               geom = "errorbar",
               linetype = 1,
               width = 0.2) +
  geom_boxplot(outliers = FALSE) + #do not show outliers, this is shown by jitter
  facet_wrap2(~ Aphid_species,
             nrow = 1,
             strip = strip0,
             labeller = labeller(Aphid_species = c(Bb = "Bb", Mp = "gMp", MpN = "rMp"))) +
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  stat_summary(fun = mean,
               geom = "point",
               size = 1.5,
               color = "gray30",
               fill = "white",
               shape = 23) + #Shows the mean as a white circle
  geom_segment(aes(x = 0.8, y = 15, xend = 2.2, yend = 15)) +
  geom_text(data = DataSum_All_8d,
            aes(label = Letters, y = 18, x = Soil_conditioning), # fill out the significant letters
            size = 4,
            hjust = -3,
            #position = position_dodge(0.9)
           ) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     #breaks = seq(0, 25, 5), #steps on the y-axis
                     limits = c(0, 1.25*max(data = data[data$Days_after_inf == 14, "Aphid_number"]))) +   #y limits
  scale_fill_manual(values = c("#882255", "#009E73")) + # Manually change the colors of the bars. You need to define fill in second line of the plot script to get it working; c("#009E73", "#56B4E9")
  ylab("Number of aphids on day 8") +    #y-label with Mp in italic
  xlab("Soil treatment") +
  ggtitle(Stats_All_8d) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")

mapply(function(x)
  ggsave(plot = last_plot(),
         filename = x,
         path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
         scale = 2.2,
         width = 5,
         height = 4,
         units = "cm",
         dpi = 300),
  x = c("FP_Aphid_number_All_8d_high.svg", "FP_Aphid_number_All_8d_high.png"))
```

## All aphid species 14 days
```{r, fig.width=5, fig.height=4}
ggplot(data = data[data$Days_after_inf == 14, ],
       mapping = aes(y = Aphid_number, x = Soil_conditioning, fill = Soil_conditioning)) +
  stat_boxplot(aes(y = Aphid_number, x = Soil_conditioning), 
               geom = "errorbar",
               linetype = 1,
               width = 0.2) +
  geom_boxplot(outliers = FALSE) + #do not show outliers, this is shown by jitter
  facet_wrap2(~ Aphid_species,
             nrow = 1,
             strip = strip0,
             labeller = labeller(Aphid_species = c(Bb = "Bb", Mp = "gMp", MpN = "rMp"))) +
  geom_jitter(width = 0.25,
              height = 0,
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  stat_summary(fun = mean,
               geom = "point",
               size = 1.5,
               color = "gray30",
               fill = "white",
               shape = 23) + #Shows the mean as a white circle
  geom_segment(aes(x = 0.8, y = 48, xend = 2.2, yend = 48)) +
  geom_text(data = DataSum_All_14d,
            aes(label = Letters, y = 51, x = Soil_conditioning), # fill out the significant letters
            size = 4,
            hjust = -3,
            #position = position_dodge(0.9)
           ) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     #breaks = seq(0, 25, 5), #steps on the y-axis
                     limits = c(0, 1.2*max(data = data[data$Days_after_inf == 14, "Aphid_number"]))) +   #y limits
  scale_fill_manual(values = c("#882255", "#009E73")) + # Manually change the colors of the bars. You need to define fill in second line of the plot script to get it working; c("#009E73", "#56B4E9")
  ylab("Number of aphids on day 14") +    #y-label with Mp in italic
  xlab("Soil treatment") +
  ggtitle(Stats_All_14d) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "none")

mapply(function(x)
  ggsave(plot = last_plot(),
         filename = x,
         path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
         scale = 2.2,
         width = 5,
         height = 4,
         units = "cm",
         dpi = 300),
  x = c("FP_Aphid_number_All_14d.svg", "FP_Aphid_number_All_14d.png"))
```

## All aphid species 8 and 14 days
```{r, fig.width=6, fig.height=4}
data$Days_after_inf <- as.factor(data$Days_after_inf)
DataSum_All_8_14d$Days_after_inf <- as.factor(DataSum_All_8_14d$Days_after_inf)


ggplot(data = data,
       mapping = aes(y = Aphid_number, x = Days_after_inf, fill = Soil_conditioning)) +
  stat_boxplot(aes(y = Aphid_number, x = Days_after_inf), 
               geom = "errorbar",
               position = position_dodge(0.9),
               linetype = 1,
               width = 0.2) +
  geom_boxplot(position = position_dodge(0.9),
               outliers = FALSE) + #do not show outliers, this is shown by jitter
  facet_wrap2(~ Aphid_species,
             nrow = 1,
             strip = strip0,
             labeller = labeller(Aphid_species = c(Bb = "Bb", Mp = "gMp", MpN = "rMp"))) +
  geom_jitter(aes(group = Soil_conditioning),
              position = position_jitterdodge(jitter.width = 0.2, 
                                              dodge.width = 0.9,
                                              jitter.height = 0),
              color = "black",
              alpha = 0.2) + # Transparency is regulated with the alpha argument
  stat_summary(aes(group = interaction(Days_after_inf, Soil_conditioning)),
               fun = mean,
               geom = "point",
               position = position_dodge(0.9),
               size = 1.5,
               color = "gray30",
               fill = "white",
               shape = 23) + #Shows the mean as a white circle
  geom_segment(aes(x = 0.6, y = 15, xend = 1.4, yend = 15)) +
  geom_segment(aes(x = 1.6, y = 48, xend = 2.4, yend = 48)) +
  geom_text(data = DataSum_All_8_14d,
            aes(label = Letters, y = Height, x = Days_after_inf), # fill out the significant letters
            size = 4,
            hjust = 0.5,
            #position = position_dodge(0.9)
           ) +
  scale_y_continuous(expand = c(0, 0),        #start graph at y = min and x = min
                     #breaks = seq(0, 25, 5), #steps on the y-axis
                     limits = c(0, 1.2*max(data = data$Aphid_number))) +   #y limits
  scale_fill_manual(values = c("#882255", "#009E73"),
                    name = "Soil conditioning") + # Manually change the colors of the bars. You need to define fill in second line of the plot script to get it working; c("#009E73", "#56B4E9")
  ylab("Total number of aphids") +    #y-label with Mp in italic
  xlab("Days after infestation") +
  ggtitle(Stats_All_8_14d) +
  theme(panel.background = element_rect(fill = "white"), #theme of the graph
        panel.border = element_blank(),
        axis.line = element_line(), #show line for x and y axis
        plot.title = element_text(size = 10, hjust = 0),
        axis.text = element_text(size = 13, color = "black"),
        axis.title = element_text(size = 16),
        axis.title.x = element_text(vjust = -0.5),
        axis.title.y = element_text(vjust = 2.5), #, hjust = -0
        strip.text = element_text(size = 13),
        plot.margin = margin(5.5, 12, 5.5, 5.5, "points"),
        legend.position = "right")

mapply(function(x)
  ggsave(plot = last_plot(),
         filename = x,
         path = "C:/Users/kreek001/OneDrive - Wageningen University & Research/Chapters/Experimental Chapter 1/R_Scripts/Final_figures",
         scale = 2.2,
         width = 6.7,
         height = 4,
         units = "cm",
         dpi = 300),
  x = c("FP_Aphid_number_All_8_14d.svg", "FP_Aphid_number_All_8_14d.png"))
```
